Title here

### 2016-12-06 portfolio/text/ms.Rmd
Edit results

Trends in fishing revenue and diversification over time for individuals fishing
commercially in Alaska (Fig. \ref{fig:ts}A) reveal some movement toward
specialization, and in particular specialization on salmon. The majority
(70--90%) of fishers hold single permits, with a slight increase in single
permit holders since around 2000 (Fig. \ref{fig:ts}C). This overall trend is
most sensitive to individuals with halibut or salmon licenses --- halibut permit
owners most often have multiple permits whereas salmon permit holders tend to be
single permit holders more than individuals with permits for other fisheries
(Fig. \ref{fig:ts}C). Although the majority of individuals hold single permits,
multiple permit holders make approximately half of the overall revenue (Fig.
\ref{fig:ts}B). Switching focus from permits owned to species landed, mean
fished species diversity declined somewhat from 1980--2000 but has since
remained steady (Fig. \ref{fig:ts}D). However, this trend appears to be driven
by an increase in salmon specialists in the 1980s and 1990s --- the trend
disappears if salmon license holders are excluded (Fig. \ref{fig:ts}D).

We observed a clear exponential decrease in revenue variability for strategies
(groups of permits) with higher mean fished species diversity (Fig.
\ref{fig:across}). Strategies with one unit higher mean species diversity had
on average
`r h1[[2]]`% (`r h1[[1]]`--`r h1[[3]]`% 95% CI) 
lower standardized variability. This pattern looks qualitatively similar with or
without individuals fishing salmon. The gillnet fishery for herring roe and the
king crab fishery had the highest estimated revenue variability. Most of the
strategies with the lowest estimated revenue variability combined halibut and
salmon permits and had high levels of fished species diversity (Fig.
\ref{fig:across}).

Comparing single permit holders to other individuals holding that same permit
plus one or more other permits illustrates the expected reduction in revenue
variability from perching additional permits (Fig. \ref{fig:spokes},
Fig. S\ref{fig:spoke-all}). For example, individuals fishing on a halibut longline
permit plus an additional permit always had lower expected revenue variability
compared to individuals fishing only a halibut longline permit 
(median reduction of `r 100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR], Fig.
\ref{fig:spokes}A). Likewise, adding a permit to a herring roe gillnet permit
substantially reduced expected revenue variability. Adding permits also usually
resulted in higher expected revenue, although the permits themselves represent
a significant expense (e.g. XX).

In contrast to the clear effect of species diversity on revenue variability when
comparing across fishing strategies, the effect of changing fished species
diversity for an individual *within* the constraints of a given permit set is
more variable (Fig. \ref{fig:within}). After accounting for fishing effort (Fig.
S\ref{fig:fe}), specializing (decreasing species diversity) tends to be
associated with increased revenue (`r g2_dens`% probability; Fig.
\ref{fig:within}). This was particularly clear for permits where individuals
tend to specialize on sockeye salmon: individuals with setnet permits for salmon
in Prince William Sound, Cook Inlet, Kodiak, Bristol Bay, or the Alaska
Peninsula experienced a ~1.5% increase in revenue for a 1% decrease in fished
species diversity (Fig. \ref{fig:within}B). The converse was usually true ---
generalizing tends to be associated with lower expected revenue after accounting
for fishing effort (i.e. Fig. \ref{fig:within}A and \ref{fig:within}B are nearly
mirror images left to right). This specializing benefit on revenue is only
apparent after accounting for fishing effort. Given that fishing for more
species tends to be associated with increased fishing effort, generalizing tends
to be associated with higher revenue when not standardizing for fishing effort
(Fig. S-TODO).

After accounting for fishing effort, adjusting (increasing or decreasing) one's
fished species diversity within the constraints of a permit set tends to be
associated with greater expected variability or uncertainty in year-to-year
revenue (Fig. \ref{fig:within} strategies above 0, Fig. S\ref{fig:fe}). This
effect was strongest for individuals with a halibut longline permit or halibut
and sablefish longline permits. Individuals with these strategies experienced
~2% increase in standardized variability for a 1% change in fished species
diversity. Fished species diversity for these permits is primarily in the form
of bycatch.

The Alaskan halibut and sablefish fisheries were rationalized in 199X --- they
switched from XX to a individual fishery quota (IFQ) system. We refit our
models allowing all effects to vary separately before and after 19XX for
strategies involving these permits (i.e. treating them as separate strategies).
Variability was reduced by ~25% (XX--XX 95% CI) after the introduction of these
IFQs compared to before for individuals with only a halibut or sablefish permit
(Fig. S\ref{fig:ifq}A). The cost of changing fished species diversity for an
individual in terms of the effect on revenue variability increased after the
introduction of IFQs for most strategies, and especially for individuals fishing
only halibut and sablefish (Fig. S\ref{fig:ifq}B).

>>>>

Trends in fishing revenue and diversification over time for individuals fishing
commercially in Alaska (Fig. \ref{fig:ts}A) reveal a transition toward
specialization, and in particular specialization on fishing salmon. The majority
(70--90%) of fishers hold single permits, with a slight increase in
single-permit holders since ~2000 (Fig. \ref{fig:ts}C). This overall trend is
most sensitive to halibut or salmon permit holders --- compared to other
fisheries, halibut permit holders are more likely to hold multiple permits
whereas salmon permit holders are more likely to be single permit holders (Fig.
\ref{fig:ts}C). Despite making up only 10--30% of the individuals, multiple
permit holders make approximately half the overall revenue (Fig. \ref{fig:ts}B).
The mean fished species diversity of this revenue declined somewhat from
1980--2000 but has since remained steady (Fig. \ref{fig:ts}D). However, this
trend appears to be driven by an increase in salmon specialists in the 1980s and
1990s --- the trend disappears if salmon license holders are excluded (Fig.
\ref{fig:ts}D).

We observe a clear exponential decrease in revenue variability for strategies
(groups of permits) with higher mean fished species diversity (Fig.
\ref{fig:across}). Strategies with one unit higher mean effective species
diversity had on average `r h1[[2]]`% (`r h1[[1]]`--`r h1[[3]]`% 95% CI) lower
standardized variability. This pattern looks qualitatively similar with or
without individuals targeting salmon. The gillnet fishery for herring roe and
the king crab fishery had the highest estimated revenue variability. Most of the
strategies with the lowest estimated revenue variability combined halibut with
a salmon permit and had high levels of fished species diversity (Fig.
\ref{fig:across}).

Comparing single permit holders to other individuals holding that same permit
plus one or more other permits illustrates the expected reduction in revenue
variability from purchasing additional permits (Fig. \ref{fig:spokes}, Fig.
S\ref{fig:spoke-all}). For example, individuals fishing a halibut longline
permit plus one additional permit always had lower expected revenue variability
compared to individuals fishing only a halibut longline permit (median reduction
of `r 100-spoke[[2]]`% [`r 100-spoke[[3]]`--`r 100-spoke[[1]]`% IQR], Fig.
\ref{fig:spokes}A). Likewise, adding a permit to a herring roe gillnet strategy
substantially reduced expected revenue variability (Fig. \ref{fig:spokes}B).
Adding permits also usually resulted in higher expected revenue, although the
permits themselves represent a significant expense (e.g. XX).

In contrast to the clear across-strategy effects of species diversity on revenue
and revenue variability, the effect of changing fished species diversity for an
individual *within* the constraints of a given permit set is more variable (Fig.
\ref{fig:within}). After accounting for fishing effort (Fig. S\ref{fig:fe}),
specializing (decreasing species diversity) tends to be associated with
increased revenue (`r g2_dens`% probability; Fig. \ref{fig:within}). This is
particularly clear for permits where individuals tend to specialize on sockeye
salmon: individuals with setnet permits for salmon in Prince William Sound, Cook
Inlet, Kodiak, Bristol Bay, or the Alaska Peninsula experience a ~1.5% increase
in revenue for a 1% decrease in fished species diversity (Fig.
\ref{fig:within}B). The converse is also usually true --- generalizing tends to
be associated with lower expected revenue after accounting for fishing effort
(i.e. Fig. \ref{fig:within}A and \ref{fig:within}B are near mirror images left
to right). This specializing benefit for revenue is only apparent *after*
accounting for fishing effort. Given that fishing for more species tends to be
associated with increased fishing effort, generalizing tends to be associated
with higher revenue when not standardizing for fishing effort (Fig. S-TODO).

After accounting for fishing effort, adjusting (increasing or decreasing) an
individual's fished species diversity within the constraints of a permit set
tends to be associated with greater expected variability or uncertainty in
year-to-year revenue (Fig. \ref{fig:within} strategies above 0; Fig.
S\ref{fig:fe}). This effect was strongest for individuals with a halibut
longline permit or halibut and sablefish longline permits. Individuals with
these strategies experienced ~2% increase in standardized variability for a 1%
change in fished species diversity (Fig. \ref{fig:within}). Fished species
diversity levels above one for these permits is primarily due to bycatch.

The Alaskan halibut and sablefish fisheries were "rationalized" in 199X --- they
switched from XX to an individual fishery quota (IFQ) system. We refit our
models allowing all effects to vary separately before and after 1995 for
strategies involving these permits (i.e. treating them as separate strategies).
The introduction of IFQs reduced variability by ~25% (XX--XX 95% CI) for
individuals with only a halibut or sablefish permit (Fig. S\ref{fig:ifq}A). For
most strategies, the effect of increased revenue variability associated with
changing fished species diversity became stronger after the introduction of IFQs
(Fig. S\ref{fig:ifq}B). This was especially true for individuals fishing only
halibut or sablefish (Fig. S\ref{fig:ifq}B).
